
%from pep 2.1, paragrafos 12, 13
Amirani et al.  \cite{amirani_new_2008} appear to be the first 
to provide a viable alternative to classical data carving tools using a neural network approach. Two previous works were found using neural networks with data carving related goals, by Dunham et al. \cite{dunham_classifying_2005} and Harris \cite{harris_using_2007}, but the first worked with encrypted files only and the second did not achieve good results.

%from pep 2.1, paragrafos 14
Amirani et al.  \cite{amirani_new_2008} used Principal Component Analysis (PCA) as input for a 5 layer feed-forward auto-associative unsupervised neural network to do feature extraction and a 3 layer Multilayer Perceptron (MLP) to perform classification. They used a similar approach in 2013 \cite{amirani_feature-based_2013}.
\sigla{PCA}{Principal Component Analysis}
\sigla{MLP}{Multilayer Perceptron}

%from pep 2.1, paragrafos 16,17,18
Other works were found applying neural networks to perform data carving, also using some form of dimensionality reduction as PCA. Ahmed et al. \cite{ahmed_content-based_2010}\cite{ahmed_fast_2011} used byte frequency, 
Penrose et al. \cite{penrose_approaches_2013} used compression rate,
and Maslim et al. \cite{maslim_distributed_2014} used PCA, as did Amirani et al.  \cite{amirani_new_2008}.

%from pep 2.1, paragrafos 15
Xu and Dong \cite{xu_reassembling_2009} used a neural network as a cluster reassembling technique for JPEG image fragments.

%from pep 2.1, paragrafos 19
Hiester \cite{hiester_file_2018} apparently was the first to not resort to dimensionality reduction and also the first to utilize an LSTM network to perform file fragment classification. He compared results using three types of neural networks: feedforward, convolutional, and long short-term memory. The goal was to classify the data type of individual sectors (512 bytes), considering four file types: CSV, XML, JPG and GIF.

% Table \ref{tab:datacarvingstudies} summarizes the  machine learning techniques used in each data carving study.
% \input{content/tables/3.3-table-studies.tex}