% \levelC{Objective}
In the previous chapter, it was observed that file types that use compression or contain images have a higher negative impact on accuracy than other file types do. This raises the question of whether high entropy may be related to the observed errors.

Before conducting experiments related to the cause of errors, a list of conceivable error sources (E1 to E5) was elaborated:
\begin{enumerate}[itemindent=\parindent,label=\textbf{E\arabic*.}]
    \item For some data structure, the model cannot distinguish it from random data. This can happen if the pattern in the data is too complex, beyond the capabilities of the model. It may be the case that in practice no model can perform this distinction or, instead, this may be a limitation of this particular model only. This situation may occur in files that use compression or cryptography, or more generally, any file type with high entropy.
    
    \item Different file types using different data structures, but the model cannot distinguish between them. In this case the model can perceive that there are structures in the data, but it is not able to differentiate them.

    \item Different file types using the same data structure. It is common for a given file type to employ different types of data structures. If two or more file types make use of the same data structure, the existence of that structure will then not be sufficient to differentiate those file types, as it may belong to any one of them.
    The reverse, a file type that uses multiple kinds of data structures, does not constitute a problem as it simply results in extra work during the model training.

    \item Same file type with multiple extensions. If the same file type appears in the dataset with multiple extensions, ``JPG'' and ``JPEG'' for example, the model will not be able to predict which label is used in the validation dataset for a given instance, since this distinction exists in the labeling but not in the content.

    \item Files that contain other files. Some file types need to embed other files. If the inner file is categorized, even if the model finds an unmistakable pattern, it will not match the label, which will be the extension of the outer file. A ``PDF'' file, for example, can embed a ``JPG'' file. If the model predicts ``JPG'' as the class of a portion of this file, it will not match the instance label on the dataset, which would be ``PDF''.
\end{enumerate}

The first error source, E1, is the focus of this section. In the file fragment classification task, it is expected that some portion of the classifications errors of a given model be caused by its inability to recognize patterns in the data if the data has high entropy. In these situations, even humans may be unable to tell if a sample is valid or if it is random data.

The second error source, E2, is a situation that could be improved by a better model or more training. Since the model has successfully detected structures, it is conceivable that avoiding misinterpretation of one structure as another is possible. This error source is not explored in this study.

The three last error sources listed above, E3 to E5, are not explored in this study. They are similar in nature, as the last two may be viewed as special cases of E3. 

% \levelC{Hypothesis}
The goal of this experiment is to test the \textbf{hypothesis that part of the errors of file fragment classification can be explained by the existence of data that has no structure detectable by the model}. Not all file types possess this kind of data, and on those that do, they should compose only a portion of the file.

